\documentclass{article}

\usepackage{mydocument}
\usepackage{myscience}

\title{Kale Kundert}
\author{2325 Bryant Street\\San Francisco, CA 94110\\(650) 814-8603}
\date{}

\begin{document}

 \maketitle

 \pagestyle{empty}
 \thispagestyle{empty}

 \section*{Research Goals}

  Protein design can be succinctly defined as the search for sequences that are 
  compatible with some desired 3D structure.  Computational design methods 
  currently evaluate only the single lowest energy structures predicted for 
  each sequence.  While this approach has led to a remarkable number of 
  successful designs, the incorrect assumption that proteins adopt a single 
  ground state has become limiting.  In reality, proteins occupy an ensemble of 
  different conformations in their ground states.  These ground state ensembles 
  are intimately involved in processes like allostery, binding, and even 
  catalysis.  To incorporate phenomena like these into future designs, protein 
  design must be redefined as the search for sequences that are compatible with 
  some desired ensemble.

 \section*{University Education}

  \begin{description}
   \item[University of California, San Francisco] Began pursuing a doctoral 
   degree in biophysics in the Fall of 2011.  Currently working under the 
   mentorship of Tanja Kortemme.
   
   \item[University of California, Berkeley] Attended from the Fall of 2009 to
   the Spring of 2011.  Earned a 3.84 GPA and graduated with a Bachelor of 
   Science degree in the field of chemical biology.
   
   \item[Foothill Community College] Attended from the Fall of 2007 to the
   Spring of 2009.  Completed 113 quarter units and earned a 3.93 GPA.
  \end{description}

 \section*{Academic Awards}

  \begin{description}
   \item[\href{http://chemistry.berkeley.edu/commencement/address/pdf/commencement-program-2011.pdf}{Hypercube 
   Scholar Award}] Earned in the spring of 2011 upon graduation from Berkeley.  
   Awarded by the College of Chemistry to the student with the most promise in 
   the field of computational chemistry.
  \end{description}

 \section*{Research Experience}

  \begin{description}
   \item[Ensembles in Protein Design] Currently working with the Kortemme group 
   to rationally manipulate protein conformational ensembles.  The project has 
   required knowledge of statistical mechanics and the Rosetta protein design 
   software suite.
   
   \item[Light-Switchable MmCpn] Worked with the Kortemme group to develop a 
   computational protocol to predict regions within proteins where small 
   perturbations will significantly affect dynamics.  This protocol was applied 
   to the design of a light-switchable variant of the MmCpn chaperonin.  
   %Gained experience using libraries for linear algebra and normal mode analysis.

   \item[\textkappa{}-Opioid Receptor Ligands] Worked with the Shoichet group 
   to computationally screen for novel ligands of the \textkappa{}-opioid 
   receptor. 
   %Gained experience performing ligand docking calculations and running jobs on 
   %a cluster.

   \item[Site-Specific Protein Crosslinking] Worked with the Francis group to 
   build compounds composed of anilines and aminophenols that could be used to 
   make very selective cross-links between proteins. 
   %Gained experience performing organic synthesis.

   \item[Antibacterial Phage Capsids] Spent time in the Francis
   group working to create a phage with targetable antibiotic properties.
   %Gained experience running bioconjugation reactions and building peptides 
   %using solid-phase techniques.
  \end{description}

 \section*{Volunteer Experience}
  
  \begin{description}
   \item[Science \& Health Education Partnership] Designed six science lessons 
   for a fourth-grade class at Leonard Flynn Elementary.  The lessons used 
   geology to teach about careful observation and the scientific method.  

   \item[Boys and Girls Club] Volunteered as a one-on-one after-school tutor at 
   the San Mateo Boys and Girls Club.  Our goals as tutors were to provide a 
   supportive environment for students to do homework and to foster good study
   habits.
   
   \item[Organic Chemistry Tutor] Volunteered as an organic chemistry tutor for 
   students at Foothill Community College.  Learned about the importance and 
   difficulty of clearly presenting complex information.
  \end{description}

 %\section*{Programming Experience}

 % \begin{description}
 %  \item[Python] Seven years and 150,000 lines of experience.  Familiar with
 %  matrix analysis, integration into C and C++, and PyMol scripting.

 %  \item[Fortran, C, C++, Java] Fluent in all these languages.  Capable of 
 %  choosing the appropriate language for different tasks.
 % \end{description}

\end{document}
