\section{Research Experience}

\subsection{Postdoctoral}

\begin{description}[leftmargin=10mm, labelindent=5mm]

\item[Recombinase target specificity (Church lab, 2019 to present)]
      Developing high throughput assays to rigorously evaluate algorithms for 
      protein/DNA interface design, with the ultimate goal of developing 
      improved algorithms and designing variants of Cre recombinase that 
      specifically target therapeutically relevant sites in the human genome.

\end{description}

\subsection{Doctoral}

\begin{description}[leftmargin=10mm, labelindent=5mm]

\item[Regulating Cas9 with small molecules (Kortemme Lab, 2015 to 2019)]
        Used rational design and directed evolution to insert aptamer domains 
        into the guide RNA of the CRISPR/Cas9 system so as to make the entire 
        system sensitive to the presence or absence of certain small molecules.  
        We hope this tool will allow scientists to more easily probe and design 
        genetic circuits in all kinds of cells.

\item[Positioning functional protein residues (Kortemme Lab, 2014 to 2019)]
        Developed an algorithm to predict protein sequences that will fold into 
        a desired active site conformation, especially in cases where this 
        would require rearrangement of the backbone.  Applying this method to 
        probe the active site of ketosteroid isomerase (KSI) and to expand the 
        range of sites that can be targeted by CRISPR/Cas9.

\item[Ensembles in protein design (Kortemme Lab, 2012 to 2014)] 
        Developed algorithms for sampling protein conformational ensembles 
        without bias (e.g.\ obeying detailed balance).  Worked to apply these 
        algorithms to the rational design of allosteric proteins.

\item[Rosetta protein design suite (Rosetta Commons, 2012 to present)] 
        Improving the Rosetta protein design suite as a core developer.  
        Rosetta is the preeminent software suite in the field of protein design 
        and has been licensed to over 40 companies and 19,000 academic users to 
        date.

\item[Multiscale integrated modeling (Šali Lab, 2012)]
        Developed a method to build models of large protein complexes by 
        integrating experimental data and physical knowledge from many 
        different length scales.

\item[Virtual screening of GPCR ligands (Shoichet Lab, 2012)]
        Computationally screened for novel ligands of the κ-opioid receptor.

\end{description}

\subsection{Undergraduate}

\begin{description}[leftmargin=10mm, labelindent=5mm]

\item[Site-specific protein crosslinking (Francis Lab, 2010-2011)] 
        Synthesized compounds composed of anilines and aminophenols that could 
        be used to make selective cross-links to oligomerize specific proteins 
        and to test hypotheses in molecular and systems biology.

\item[Antibacterial phage capsids (Francis Lab, 2009-2010)]
        Assisted on a project to create a modified phage capsid with targetable 
        antibiotic properties and low immunogenicity.

\end{description}


